---
title: ""
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(flexdashboard)

```

### Instructions 

The aim of this assignment is to provide you with an opportunity to sharpen your skills in using ggplot(). While some of the plots you create may resemble those we covered in class, it is essential that they are original. 
 
 Rules for the Assignment:
 
 1.All data sets except iris are fair game. That includes past data sets used in the class, sets built into R, your own data, and even online data.
 
 2. All graphs must include axis labels, plot title, a theme of your choice, and a brief description/interpretation of the plot (2-3 sentences).


It's worth noting that ggplot() is a widely-used tool, and there are numerous online resources available for you to explore. We strongly recommend that you take advantage of these resources to deepen your understanding of ggplot(). 

Knit the document into a PDF and submit it to Canvas by 02/28/2024 at 11:59 pm.


```{r echo = FALSE}
####
#00 - Load Packages and Data#
####
library(knitr)
library(tidyverse)
library(ggplot2)
library(ggthemes)

```


### 1. Make a Scatter Plot With Customized Point Size and Transparency. (3pts)
```{r,fig.width=10, fig.height=5}
####
#01#
####

iris %>%
  ggplot(aes(x = Petal.Length, y = Petal.Width, color=Species)) +
  geom_point() +
  labs(x = "Petal Length", y = "Petal Width", 
       title = "Petal Width vs. Petal Length") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_stata() +
  scale_color_brewer("Species", palette="Dark2") +
  scale_x_continuous (name= "Petal Length (cm)", breaks=seq(3.0, 7.0, 2.0),limits = c(3,7)) +
  scale_y_continuous(name="Petal Width (cm)", breaks = seq(1.0, 2.5, 0.25), limits=c(1.0,2.5))


```

***
Description and Interpretation:



### 2. Fit a Line Through Your Scatter Plot From 1. (3pts)
```{r}
####
#02#
####
#your code here

```

***

Description and Interpretation:


### 3. Set the transparency, shape, and color of your graph from 1 based on expressions. Scale the color. (3pts)
```{r}
####
#03#
####
#your code here

```

***

Description and Interpretation:


### 4. Make a Boxplot With Customized Boxplot Width. (3pts)
```{r}
####
#04#
####
#your code here

```
***
Description and Interpretation:


### 5. Overlay the Individual Points Over Your Box Plot From 3. and Adjust the Point Size and Transparency as Needed. (3pts)
```{r}
####
#05#
####
#your code here

```
***
Description and Interpretation:


### 6. Make a Plot and Modify the Scale in a Beneficial Way Using Scalar Functions. Explain the How the Change Improved the Graph. (4pts) 
```{r}
####
#06#
####
#your code here

```
***
Description and Interpretation:


### 7. Make a New (don't use any plots from 1-4) Plot With facet_wrap(). (4pts)
```{r}
#07#
####
#your code here

```
***
Description and Interpretation:


### 8. Using the Plot From 5, Scale the Colors and Reorder Your Facet to Reverse Order. (4pts)
```{r}
#08#
####
#your code here

```
***
Description and Interpretation:


### 9. Make a Plot Using a Geometry That Was Not Covered in Class. (4pts)
```{r}
####
#09#
####
#your code here 
```
***
Description and Interpretation:


### 10. Make a Plot Using a ggplot Extension That Was Not Covered in Class. Explain what the extension does.. (4pts)
```{r}
####
#10#
####
#your code here 
```
***
Description and Interpretation:


### Appendix

```{r show-code, ref.label = all_labels(), echo = TRUE, eval = FALSE}

```



