---
title: "Introduction to R Programming: Directory Management and File Operations"
author: "Updated from Shady Kuster's Tutorial"
date: "2025-02-10"
output: pdf_document
---

## Getting Started 

Before we begin, let's set up our environment. Run this code block to load the required packages:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(fs)

# If you get an error about missing packages, uncomment and run these lines:
# install.packages("stringr") 
# install.packages("fs")
```

## Understanding Directories: Your Computer's Filing System 

Think of your computer like a filing cabinet:
- A **directory** is just another word for a folder
- Files are stored inside directories
- Directories can contain other directories (like folders within folders)

### What is a Working Directory? 

Your working directory is like your "current location" in the filing cabinet. When you tell R to read or create a file, it will look in this location by default.

Let's find out where we are:

```{r}
# This shows your current location
current_location <- getwd()
print(current_location)
```

### Moving Between Directories 

You can move to a different directory using `setwd()`. For example:

```{r, eval=FALSE}
# Moving to your Documents folder
setwd("Documents")  # On Mac
# or
setwd("C:/Users/YourName/Documents")  # On Windows
```

ðŸ’¡ **Important Tips for Beginners:**
1. Use forward slashes (/) even on Windows
2. Directory names are case-sensitive ("Documents" â‰  "documents")
3. Always check your working directory if files aren't being found

## Working with Files 

### Creating a Simple Text File

Let's write a friendly message to a file:

```{r}
message <- "Hello! This is my first R-created file!"
write(message, "MyFirstFile.txt")
```

### Reading Files

Now let's read the file we just created:

```{r}
# Read and display the file contents
content <- readLines("MyFirstFile.txt")
print(content)
```

## Practice Exercise: Directory Navigation ï¸

Let's create a simple project structure:

1. Create a folder called "my_first_project"
2. Inside it, create two folders: "data" and "results"
3. Navigate between them using R

```{r, eval=FALSE}
# First, go to your Documents folder
setwd("~/Documents")  # or your preferred location

# Create directories
dir.create("my_first_project")
dir.create("my_first_project/data")
dir.create("my_first_project/results")

# Move into the project folder
setwd("my_first_project")

# Check what folders exist here
list.files()
```

## Variables in R: Storing Information 

Think of variables like labeled boxes where you store things:

```{r}
# Storing a number
my_age <- 25
print(my_age)

# Storing text
my_name <- "Alex"
print(my_name)

# Storing multiple numbers
measurements <- c(10, 15, 20, 25, 30)
print(measurements)

# Calculate average
average <- mean(measurements)
print(average)
```

## Common Problems and Solutions ðŸ”§

1. **File Not Found Error?**
   - Check your working directory with `getwd()`
   - Make sure file name spelling matches exactly
   - Verify file exists in current directory with `list.files()`

2. **Path Issues?**
   - Always use forward slashes (/)
   - Check for typos in directory names
   - Verify full path with `file.path()`

## Next Steps 

Practice these concepts by:
1. Creating different directories
2. Moving between them using `setwd()`
3. Creating and reading files in different locations
4. Using variables to store and manipulate data

Remember: Programming is like learning a new language - practice makes perfect! Don't worry if everything doesn't make sense immediately. ðŸ’ª

---

## Additional Resources 

- R for Beginners: [https://www.r-project.org/other-docs.html](https://www.r-project.org/other-docs.html)
- RStudio Primers: [https://rstudio.cloud/learn/primers](https://rstudio.cloud/learn/primers)
- R Markdown Guide: [https://rmarkdown.rstudio.com/lesson-1.html](https://rmarkdown.rstudio.com/lesson-1.html)
