---
title: "Getting Started with R: Understanding Files and Folders"
author: "Updated from Shady Kuster's Tutorial"
date: "2025-02-10"
output: pdf_document
---

## Setup

First, let's get our tools ready:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(fs)

# If you need to install packages, uncomment these lines:
# install.packages("stringr") 
# install.packages("fs")
```

## Part 1: Understanding Your Computer's Organization 

### Key Terms
- **Directory** = Folder
- **Working Directory** = The folder R is currently looking at
- **Path** = The address that tells R where to find a file or folder

### Checking Your Location

Let's find out where R is currently looking:

```{r}
# This shows your current location
getwd()  # "get working directory"
```

### Moving to a New Location

To move to a different folder:

```{r, eval=FALSE}
# Example: Moving to Documents folder
setwd("Documents")  # For Mac
# OR
setwd("C:/Users/YourName/Documents")  # For Windows
```

### **Important Tips:**
1. Always use forward slashes (/) even on Windows
2. Capitalization matters! "Documents" is different from "documents"
3. Keep paths inside quotes: `setwd("Documents")`

## Part 2: Creating Your Project Structure ️

Let's set up a simple folder structure:

```{r, eval=FALSE}
# Store your Documents path
my_docs <- "/Users/YourName/Documents"  # Change this to your path!

# Create project folders
dir.create(file.path(my_docs, "courses"))
dir.create(file.path(my_docs, "courses/genetics"))
dir.create(file.path(my_docs, "courses/cell bio"))
dir.create(file.path(my_docs, "courses/calculus"))
```

## Part 3: Working with Files 

### Creating a File

```{r}
# Write a simple message to a file
message <- "Hello from R!"
write(message, "hello.txt")
```

### Reading a File

```{r, eval=FALSE}
# Read the file we just created
content <- readLines("hello.txt")
print(content)
```

## Common Problems and Solutions 

1. **File Not Found?**
   ```r
   # Check where R is looking
   getwd()
   
   # List all files in current directory
   list.files()
   ```

2. **Wrong Directory?**
   ```r
   # Go back one folder
   setwd("..")
   
   # Go back two folders
   setwd("../..")
   ```

## Practice Exercises 

1. **Basic Navigation**
   ```r
   # Your turn! Try to:
   # 1. Go to your Documents folder
   # 2. Create a new folder called "r_practice"
   # 3. Move into that folder
   # 4. Create a file
   # 5. Read that file
   ```

2. **File Creation Challenge**
   ```r
   # Create three folders:
   # - data
   # - results
   # - scripts
   ```

## Tips for Success 🌟

1. Before running code that reads/writes files:
   - Check your working directory with `getwd()`
   - Look at available files with `list.files()`

2. Keep your work organized:
   - Use consistent folder names
   - Keep related files together
   - Document your folder structure

## Windows Users Note 🪟

Windows shows paths like this: `C:\Users\Name\Documents`
But in R, always use forward slashes: `C:/Users/Name/Documents`

## Next Steps 📚

1. Practice creating and navigating folders
2. Try reading and writing different files
3. Experiment with absolute vs relative paths

Remember: Practice makes perfect! Don't worry if you make mistakes - they're part of learning. 

Need help? Try:
- Running `?setwd` to get help on any command
- Using Google for error messages
- Asking your instructor for clarification

