---
title: "Student Datasets"
author: "CM515 2025 Students"
date: "2025-01-26"
output:
  pdf_document: default
  html_document: default
---

## Dataset previews

### Amanda
The dataset I am using for the course is a subset of saliva samples obtained from dairy calves to assess cortisone and cortisol concentrations (ng/mL) under various environmental conditions. I obtained a random subset from the larger dataset and would like to look at the relationship between cortisone and cortisol concentrations.

```{r Amanda}
# amanda_tsv_v1 = read.table('assignment_submissions/submissions/amanda-Saliva-1.txt', header=T)
# file.copy('assignment_submissions/submissions/amanda-Saliva-1.txt', 'student_dataset_previews/amanda.txt')
amanda_tsv = read.table('student_dataset_previews/amanda.txt', header=T)
# amanda_tsv == amanda_tsv_v1
head(amanda_tsv)
```

### Anais
RNA-seq of A.thaliana lines with a gene silenced related to herbicide metabolism
(dicamba). The genes are IAA and PIF4.

```{r Anais}
```

### Andrea
CFU readings I measured over time.

```{r Andrea}
library(readxl)
andrea_Dataset <- read_excel("assignment_submissions/submissions2/andrea_Dataset_CFU_1st_experiment.xlsx")
head(andrea_Dataset)
```

### Ben
It is a mRNA riboseq data set that Naly would like processed.
```{r Ben}

```

### Danielle
The data set I am using represents the area of detection of different recombinant PIN proteins expressed in Brachypodium.
```{r Danielle}
#danielle_v1 <- read_excel("assignment_submissions/submissions2/samsondanielle_LATE_357338_34472110_week 0 assignment data submisison.xlsx")
#file.copy("assignment_submissions/submissions2/samsondanielle_LATE_357338_34472110_week 0 assignment data submisison.xlsx",'student_dataset_previews/danielle.xlsx')
danielle = read_excel('student_dataset_previews/danielle.xlsx')
#all(danielle == danielle_v1)
head(danielle)
```


### Gianna

Cut&Run differential bind output for Rosenberg lab (Aedees mosquito sugar fed v bloodfed day 3)
``` {r Gianna}

gianna_data = read.table("student_dataset_previews/gianna.csv", header=T, sep=",")
head(gianna_data)
```

### Shea

TB activation and incident untargeted metabolomics datasets

```{r Shea}
shea_data = read.table('student_dataset_previews/shea.txt', header=T)
head(shea_data)

```


### Sinead 

```{r Sinead}
#sinead_v1=read.table('assignment_submissions/submissions2/cahillsinead_374726_34447066_2016-04-15 to 16 _ pin1-4 ML1 BdPINs Measurments ALL.txt', header=T)
#file.copy('assignment_submissions/submissions2/cahillsinead_374726_34447066_2016-04-15 to 16 _ pin1-4 ML1 BdPINs Measurments ALL.txt','student_dataset_previews/sinead.txt')
sinead=read.table('student_dataset_previews/sinead.txt', header=T)
#sinead_v1 == sinead
#all(sinead_v1 == sinead)
head(sinead)
```


### Susan

The dataset I will be using is a subset of data we collect that records the activity of a group of 6 mice every minute for 10-11 days. This data is outputted in an Excel data sheet. To process the data many of the columns are deleted and just tabs with mouse parameters are included.

```{r Susan}
# susan_file_path = "assignment_submissions/submissions/gogolski_DTA file for class.csv"
# susan_file_connection = file(susan_file_path)
# susan_file_peek = readChar(susan_file_connection,300) # used vi and command line to choose 300
# cat(susan_file_peek)
# susan_data_1 = read.table(susan_file_connection, header=T, sep=",", skip=1)

#file.copy("assignment_submissions/submissions/gogolski_DTA file for class.csv", "student_dataset_previews/susan.csv")
susan_data = read.table("student_dataset_previews/susan.csv", header=T, sep=',', skip=1)

# susan_data == susan_data_1 
# all(susan_data == susan_data_1 )

head(susan_data)
```
### Xuan

The data examine the different types of mutations observed through sequencing in the TRAF3 genes.

```{r Xuan}
library(readxl)
# xuan_filename = "assignment_submissions/submissions/beattyxuan_362764_34400409_Traf3mutations.xlsx"
# xuan_xls = read_xlsx(xuan_filename)
# file.copy(xuan_filename, "student_dataset_previews/xuan.txt")
xuan_data = read_xlsx("student_dataset_previews/xuan.txt")

# xuan_xls == xuan_data
# all(xuan_xls == xuan_data, na.rm = T)

head(xuan_data)
```









