---
title: "Student Datasets"
author: "CM515 2025 Students"
date: "2025-01-26"
output:
  pdf_document: default
  html_document: default
---

## Dataset previews

### Amanda
The dataset I am using for the course is a subset of saliva samples obtained from dairy calves to assess cortisone and cortisol concentrations (ng/mL) under various environmental conditions. I obtained a random subset from the larger dataset and would like to look at the relationship between cortisone and cortisol concentrations.

```{r Amanda}
amanda_tsv = read.table('student_dataset_previews/amanda.txt', header=T)
head(amanda_tsv)
```

### Anais
RNA-seq of A.thaliana lines with a gene silenced related to herbicide metabolism
(dicamba). The genes are IAA and PIF4.

```{r Anais}
```

### Andrea
CFU readings I measured over time.

```{r Andrea}
library(readxl)
andrea_Dataset <- read_excel("assignment_submissions/submissions2/andrea_Dataset_CFU_1st_experiment.xlsx")
head(andrea_Dataset)
```

### Ben
It is a mRNA riboseq data set that Naly would like processed.
```{r Ben}

```

### Danielle
The data set I am using represents the area of detection of different recombinant PIN proteins expressed in Brachypodium.
```{r Danielle}
danielle = read_excel('student_dataset_previews/danielle.xlsx')
head(danielle)
```


### Gianna

Cut&Run differential bind output for Rosenberg lab (Aedees mosquito sugar fed v bloodfed day 3)
``` {r Gianna}
gianna_data = read.table("student_dataset_previews/gianna.csv", header=T, sep=",")
head(gianna_data)
```

### Shea

TB activation and incident untargeted metabolomics datasets

```{r Shea}
shea_data = read.table('student_dataset_previews/shea.txt', header=T)
head(shea_data)

```


### Sinead 

```{r Sinead}

sinead=read.table('student_dataset_previews/sinead.txt', header=T)

head(sinead)
```


### Susan

The dataset I will be using is a subset of data we collect that records the activity of a group of 6 mice every minute for 10-11 days. This data is outputted in an Excel data sheet. To process the data many of the columns are deleted and just tabs with mouse parameters are included.

```{r Susan}

susan_data = read.table("student_dataset_previews/susan.csv", header=T, sep=',', skip=1)
head(susan_data)
```
### Xuan

The data examine the different types of mutations observed through sequencing in the TRAF3 genes.

```{r Xuan}
library(readxl)
xuan_data = read_xlsx("student_dataset_previews/xuan.txt")
head(xuan_data)
```









